---
title: "Second wave of COVID-19 in Switzerland"
author: "SGO"
date: today
format:
  html:
    toc: true
    toc-location: body
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
  docx: 
    toc: true
---

## Introduction

The aim of this exercise is to visualise the increase in the laboratory-confirmed cases of COVID-19 in Switzerland during autmn 2020.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#|output: false
# Load libraries
library(here)
library(tidyverse)
library(lubridate)
library(unibeCols)
```

```{r}
#|output: false
# Read data
cases <- read_csv(here("data/raw/COVID19Cases_geoRegion.csv"))
```

Figure 1 shows the number of laboratory-confirmed bla bla
```{r}
#|label: fig-cases
#|fig-cap: "Laboratory-confirmed cases of COVID-19 in Switzerland in 2020."
#|fig-width: 8
#|fig-height: 4
ggplot(cases, aes(x= datum, y = entries)) + geom_bar(stat = "identity", fill = unibeSaphire())
```

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
