---
title: "Body mass index of working adults in a community in Switzerland"
author: Samuel G. Okech
date: today
format:
  html:
    toc: true
    toc-location: body
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
  docx:
    toc: true
---

```{r}
#| output: false
# Load libraries
library(here)
library(tidyverse)
library(lubridate)
library(unibeCols)
library(medicaldata)
```

## Introduction

This report is based on data obtained from a section of middle-aged members of a community in Switzerland over a 20-year period (15 January, 2001 and 26 December 2020). The aim of the report is to demonstrate the relationship between body max index and age among parenting and non-parenting members of the community.


## Visualised data

@fig-inscost shows the relationship between age and body mass index of parenting and non-parenting members of a community in Switzerland.

```{r}
#| output: false
# Read data
inscosts <- read_csv(here("data/raw/insurance_with_date.csv"))
```

```{r}
inscosts_new <- inscosts %>% mutate(parenting = children>0)
```

```{r}
#| label: fig-inscost
#| fig-cap: "Relationship between age and body mass index of parenting and non-parenting members of a community in Switzerland"
#| fig-width: 8
#| fig-height: 4
ggplot(inscosts_new, aes(age, bmi, color = sex)) + geom_point() + 
  facet_wrap(~parenting) + geom_smooth(method = lm) + 
  labs(x = "Age (years)", y = "Body mass index (BMI)")
```

```{r}

```

## Conclusion

The BMI of members of this community increased with age and did not significantly differ between males and females, and between persons with or without children.

